### 2019-07-22 sc19_reviews/response.md

Figures 3 and 4 have been updated and new text added.

Reviewer 3:

Weak/strong scaling and TPS are also application and system dependent
metrics. METG differs from these metrics in that can simultaneously
(a) capture the behavior of the system at the limit of its scalability
(which is not true of weak/strong scaling) and (b) while achieving a
specified amount of useful work (which is not true of TPS). METG also
isolates the impact of changes to the communication topology at scale,
whereas in a strong scaling study this effect would be entangled with
issues of system overhead. Examples of how to compute METG from
application wall time have been added to Section 2.

METG captures the average task granularity that can be supported. It
is acceptable for some tasks to be smaller and others larger. Overhead
is a function of number of tasks times overhead per task and METG
captures this well.

The conclusion has been updated with specific insights derived from
Task Bench.

### 2019-07-22 1_introduction.tex
Fix latex build.

We present Task Bench, a benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions.  The key property of TaskBench is that it completely separates
the implementation of TaskBench for a new system to be measured from the implementation
of a new benchmark application to be run on the systems supported by TaskBench.
In all benchmarks we know of, the effort to implement $n$ benchmarks on $m$
systems is ${\cal O}(mn)$.  TaskBench's design reduce the work to ${\cal O}(m) + {\cal O}(n)$,
enbaling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems immediately run all
benchmarks.

>>>>

We present Task Bench, a benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions.  The key property of TaskBench is that it completely separates
the implementation of TaskBench for a new system to be measured from the implementation
of a new benchmark application to be run on the systems supported by TaskBench.
In all benchmarks we know of, the effort to implement $n$ benchmarks on $m$
systems is $\mathcal{O}(mn)$.  TaskBench's design reduce the work to $\mathcal{O}(m) + \mathcal{O}(n)$,
enbaling dramatically more systems and benchmarks to be explored for the same amount of programming
effort.  New benchmarks created with Task Bench
immediately run on all systems, and new systems immediately run all
benchmarks.
